A Multi-Fidelity Framework for Wildland Fire Behavior Simulations over Complex Terrain

### 2021-02-11 atmosphere-1087074-final.tex
Reorder refs

In the formal derivation of the LES equations (see, e.g,~\cite{Pope:2000,FDS_MathVal_Guides}) the filtered nonlinear terms (advection terms, mean chemical source term, and~the unresolved boundary fluxes) require subgrid-scale parameterizations.  In~this section, LES filter notation, as well as Cartesian tensor index notation, are used to clarify the terms used in the governing~equations.

@@

Here, $D_F$ is the binary diffusivity of the fuel species in air, $k_{sgs}$ is the modeled subgrid kinetic energy per unit mass discussed above, and~$g$ is the gravitational acceleration. The~constant $C_u=0.4$ is determined by matching flame height correlations across a wide range of fire Froude numbers~\cite{FDS_MathVal_Guides}.

@@

\textls[-20]{The unresolved heat flux at the surface, $\dot{q}_w''$, is determined using an \mbox{engineering approach}},
\begin{equation}
\dot{q}_w'' = h (T_g - T_w),
\end{equation}
where $h$ is the convective heat transfer coefficient, $T_w$ is the local temperature of the surface, and~$T_g$ is the temperature of the first gas phase cell off the wall.  Empirical natural/forced convection correlations are used to determine $h$:
\begin{equation}
h = \max \left[C\, |T_g-T_w|^{1/3} \; , \;
\frac{k}{L} \, \mathrm{Nu} \; , \;
\frac{k}{\delta n/2} \right],
\label{eq:qconv}
\end{equation}
where $C$ is a empirical coefficient for natural convection (1.52 for a horizontal plate and 1.31 for a vertical plane or cylinder)~\cite{Holman:1}, $L$ is a characteristic length related to the size of the physical obstruction, and~$k$ is the thermal conductivity of the gas. The~forced convection Nusselt number (Nu) depends on the geometry and flow characteristics~\cite{Holman:1,Incropera:1}.  Further details are provided in~\cite{FDS_MathVal_Guides}.

@@

@@

\bibitem[Thomas \em{et~al.}(2017)Thomas, Butry, Gilbert, Webb, and
  Fung]{thomas_2017}
Thomas, D.; Butry, D.; Gilbert, S.; Webb, D.; Fung, J.
\newblock  {The Costs and Losses of Wildfires: A Literature Review}.
\newblock In \emph{Special Publication NIST SP-1215}; National Institute of Standards
  and Technology: Gaithersburg, MD, USA,  2017.
\newblock
   {Available online: \url{https://www.nist.gov/publications/costs-and-losses-wildfires} (accessed on 05/02/2021).}

\bibitem[McDermott \em{et~al.}(2019)McDermott, Bryner, and
  Heintz]{mcdermott_2019}
McDermott, R.; Bryner, N.; Heintz, J.
\newblock  {Large Outdoor Fire Modeling (LOFM) Workshop Summary Report}.
\newblock In \emph{Special Publication NIST SP-1245}; National Institute of Standards
  and Technology: Gaithersburg, MD, USA,  2019.
\newblock
    Available online: \url{https://www.nist.gov/publications/large-outdoor-fire-modeling-lofm-workshop-summary-report} (accessed on 05/02/2021).

\bibitem[Richards \em{et~al.}(2020)Richards, Brew, and Smith]{richards_2020}
Richards, L.; Brew, N.; Smith, L.
\newblock  {2019–20 Australian bushfires—frequently asked questions: A Quick
  Guide}.
\newblock In \emph{Research Paper Series 2019-20}; Parliament of
  Australia: Canberra, Australia,  2020. ISSN 2203-5249. 
\newblock
   {Available online: \url{https://parlinfo.aph.gov.au/parlInfo/download/library/prspub/7234762/upload\_binary/7234762.pdf} (accessed on 05/02/2021).}

\bibitem[Papadopoulos and Niovi~Pavlidou(2011)]{Papadopoulos_2011}
Papadopoulos, G.D.; Niovi~Pavlidou, F.
\newblock A review of a new generation of wildfire–atmosphere modeling.
\newblock {\em IEEE Syst. J.} {\bf 2011}, {\em 5},~233--243.

\bibitem[Bakhshaii and Johnson(2019)]{Bakhshaii_2019}
Bakhshaii, A.; Johnson, E.
\newblock A review of a new generation of wildfire–atmosphere modeling.
\newblock {\em Can. J. For. Res.} {\bf 2019}, {\em
  49},~565--574.

\bibitem[Rothermel(1972)]{Rothermel:1972}
Rothermel, R.C.
\newblock A mathematical model for predicting fire spread in wildland fuels.
\newblock In \emph{Technical Report INT-115}; USDA Forest Service: Ogden, Utah,  1972.
\newblock
   {Available online: \url{http://www.treesearch.fs.fed.us/pubs/32533} (accessed on 05/02/2021).}

\bibitem[Anderson(1982)]{Anderson:1982}
Anderson, H.
\newblock {Aids to Determining Fuel Models for Estimating Fire Behavior}.
\newblock In \emph{General Technical Report INT-122}; Intermountain Forest and Range
  Experiment Station, USDA Forest Service: Ogden, Utah,  1982.
\newblock
   {Available online: \url{https://www.fs.usda.gov/treesearch/pubs/6447} (accessed on 05/02/2021).}

\bibitem[Finney(2004)]{Finney:FARSITE}
Finney, M.
\newblock {Fire Area Simulator–Model, Development and Evaluation}.
\newblock In \emph{Research Paper RMRS-RP-4 Revised}; United States Forest Service, Rocky
  Mountain Research Station, Missoula, Montana,  2004.
\newblock
   {Available online: \url{http://www.fs.fed.us/rm/pubs/rmrs\_rp004.pdf} (accessed on 05/02/2021).}

\bibitem[Bova \em{et~al.}(2015)Bova, Mell, and Hoffman]{Bova:IJWF2015}
Bova, A.; Mell, W.; Hoffman, C.
\newblock {A comparison of level set and marker methods for the simulation of
  wildland fire front propagation}.
\newblock {\em Int. J. Wildland Fire} {\bf 2015}, {\em
  25},~229--241.
\newblock{doi:10.1071/WF13178}.

\bibitem[McGrattan \em{et~al.}(2013)McGrattan, Hostikka, McDermott, Floyd,
  Weinschenk, and Overholt]{FDS_Users_Guide}
McGrattan, K.; Hostikka, S.; McDermott, R.; Floyd, J.; Weinschenk, C.;
  Overholt, K.
\newblock {\em {Fire Dynamics Simulator, User's Guide}}, 6th ed.;
\newblock National Institute of Standards and Technology: Gaithersburg,
  MD, USA; VTT Technical Research Centre of Finland: Espoo, Finland, 2013.

\bibitem[Coen(2013)]{Coen:2}
Coen, J.L.
\newblock {Modeling Wildland Fires: A Description of the Coupled
  Atmosphere-Wildland Fire Environment Model (CAWFE)}.
\newblock In~\emph{Technical Report NCAR/TN500+STR}; National Center for Atmospheric
  Research: Boulder, CO, USA, 2013.

@@

\bibitem[Lautenberger(2013)]{LAUTENBERGER_2013}
Lautenberger, C.
\newblock Wildland fire modeling with an Eulerian level set method and
  automated calibration.
\newblock {\em Fire Saf. J.} {\bf 2013}, {\em 62},~\mbox{289--298}.
\newblock {doi:10.1016/j.firesaf.2013.08.014}.

\bibitem[Mandel \em{et~al.}(2009)Mandel, Beezley, Coen, and Kim]{Mandel:2009}
Mandel, J.; Beezley, J.D.; Coen, J.L.; Kim, M.
\newblock {Data assimilation for wildland fires: Ensemble Kalman filters in
  coupled atmosphere-surface models}.
\newblock {\em IEEE Control  Syst. Mag.} {\bf 2009}, {\em 9},~47–65.
\newblock {doi:10.1109/MCS.2009.932224}.

\bibitem[Mandel \em{et~al.}(2011)Mandel, Beezley, and Kochanski]{Mandel:2011}
Mandel, J.; Beezley, J.D.; Kochanski, A.K.
\newblock {Coupled atmosphere-wildland fire modeling with WRF 3.3 and SFIRE
  2011}.
\newblock {\em \mbox{Geosci. Model} Dev.} {\bf 2011}, {\em 4},~591--610.
\newblock {doi:10.5194/gmd-4-591-2011}.

\bibitem[Mandel \em{et~al.}(2015)Mandel, Amram, Beezley, Kelman, Kochanski,
  Kondratenko, Lynn, Regev, and Vejmelka]{Mandel:2014}
Mandel, J.; Amram, S.; Beezley, J.D.; Kelman, G.; Kochanski, A.K.; Kondratenko,
  V.Y.; Lynn, B.H.; Regev, B.; Vejmelka, M.
\newblock {Recent advances and applications of WRF-SFIRE}.
\newblock {\em Nat. Hazards Earth Syst. Sci.} {\bf 2015}, {\em 14},~2829--2845.
\newblock {doi:10.5194/nhess-14-2829-2014}.

\bibitem[Kochanski \em{et~al.}(2016)Kochanski, Jenkins, Yedinak, Mandel,
  Beezley, and Lamb]{Kochanski:2016}
Kochanski, A.K.; Jenkins, M.A.; Yedinak, K.; Mandel, J.; Beezley, J.; Lamb, B.
\newblock {Toward an integrated system for fire, smoke, and air quality
  simulations}.
\newblock {\em Int. J. Wildland Fire} {\bf 2016}, {\em 25},~534–546.
\newblock {doi:10.1071/WF14074}.

\bibitem[Sethian(1999)]{Sethian:1999}
Sethian, J.A.
\newblock {\em Level Set Methods and Fast Marching Methods: Evolving Interfaces
  in Computational Geometry, Fluid Mechanics, Computer Vision, and Materials
  Science}; Cambridge University Press: Cambridge, United Kingdom, 1999.

\bibitem[Osher and Fedkiw(2006)]{Osher:2006}
Osher, S.; Fedkiw, R.
\newblock {\em Level Set Methods and Dynamic Implicit Surfaces}; Springer:  New York, United States, 2006.

\bibitem[Coen \em{et~al.}(2013)Coen, Cameron, Michalakes, Patton, Riggan, and
  Yedinak]{coen_2013}
Coen, J.L.; Cameron, M.; Michalakes, J.; Patton, E.G.; Riggan, P.J.; Yedinak,
  K.M.
\newblock WRF-Fire: Coupled Weather–Wildland Fire Modeling with the Weather
  Research and Forecasting Model.
\newblock {\em J. Appl. Meteorol. Climatol.} {\bf 2013}, {\em
  52},~16--38.
\newblock {doi:10.1175/JAMC-D-12-023.1}.

\bibitem[Mell \em{et~al.}(2007)Mell, Jenkins, Gould, and Cheney]{Mell:IJWF2007}
Mell, W.; Jenkins, M.; Gould, J.; Cheney, P.
\newblock {A physics-based approach to modelling grassland fires}.
\newblock {\em Int. J. Wildland Fire} {\bf 2007}, {\em
  16},~1--22.

@@

\bibitem[Arca \em{et~al.}(2019)Arca, G., M., M., and P.]{Arca_2019}
Arca, B.; Ghisu, T.; Casula, M.; Salis, M.; Duce, P.
\newblock A web-based wildfire simulator for operational applications.
\newblock {\em Int. J. Wildland Fire} {\bf 2019}, {\em
  28},~99--112.

\bibitem[Rehm and Baum(1978)]{Rehm:1}
Rehm, R.; Baum, H.
\newblock {The Equations of Motion for Thermally Driven, Buoyant Flows}.
\newblock {\em J. Res.  NBS} {\bf 1978}, {\em 83},~297--308.

\bibitem[McDermott and Floyd(2015)]{McDermott:2015}
McDermott, R.; Floyd, J.
\newblock {Enforcing realizability in explicit multi-component species
  transport}.
\newblock {\em Fire Saf. J.} {\bf 2015}, {\em 78},~180--187.

\bibitem[McDermott(2014)]{mcdermo_2014}
McDermott, R.J.
\newblock A velocity divergence constraint for large-eddy simulation of
  low-Mach flows.
\newblock {\em J. Comput. Phys.} {\bf 2014}, {\em
  274},~413--431.
\newblock {doi:10.1016/j.jcp.2014.06.019}.

\bibitem[Pope(2000)]{Pope:2000}
Pope, S.B.
\newblock {\em Turbulent Flows}; Cambridge University Press: Cambridge, United Kingdom, 2000.

\bibitem[Poinsot and Veynante(2005)]{Poinsot:TNC}
Poinsot, T.; Veynante, D.
\newblock {\em {Theoretical and Numerical Combustion}}, 2nd ed.; R.T. Edwards,
  Inc.: Philadelphia, PA, USA,  2005.

\bibitem[Deardorff(1980)]{Deardorff:1980}
Deardorff, J.
\newblock {Stratocumulus-capped mixed layers derived from a three-dimensional
  model}.
\newblock {\em Bound.-Layer Meteorol.} {\bf 1980}, {\em 18},~495--527.

@@

\bibitem[Bardina \em{et~al.}(1980)Bardina, Ferziger, and
  Reynolds]{Bardina:1980}
Bardina, J.; Ferziger, J.H.; Reynolds, W.C.
\newblock {Improved Subgrid Scale Models for Large Eddy Simulation}.
\newblock   In Proceedings of the  AIAA 13th Fluid \& Plasma Dynamics Conference; American Institute of
  Aeronautics and Astronautics,  Snowmass, CO, USA,   14--16 July 1980. doi:10.2514/6.1980-1357.

\bibitem[Nicoud and Ducros(1999)]{Nicoud:1999}
Nicoud, F.; Ducros, F.
\newblock {Subgrid-Scale Stress Modelling Based on the Square of the Velocity
  Gradient Tensor}.
\newblock {\em Flow Turbul.  Combust.} {\bf 1999}, {\em
  62},~183--200.

\bibitem[Maragkos and Merci(2020)]{Maragkos:2020}
Maragkos, G.; Merci, B.
\newblock On the use of dynamic turbulence modelling in fire applications.
\newblock {\em Comb.  Flame} {\bf 2020}, {\em 216},~9--23.

@@

\bibitem[Magnussen and Hjertager(1977)]{Magnussen:1}
Magnussen, B.; Hjertager, B.
\newblock {On Mathematical Modeling of Turbulent Combustion with Special
  Emphasis on Soot Formation and Combustion}.
\newblock {\em Symposium (International) on Combustion} {\bf 1977}, {\em
  16:1},~719--729.

\bibitem[McDermott \em{et~al.}(2011)McDermott, McGrattan, and
  Floyd]{McDermott:2011}
McDermott, R.; McGrattan, K.; Floyd, J.
\newblock A Simple Reaction Time Scale for Under-Resolved Fire Dynamics.
\newblock  In Proceedings of the Fire Safety Science---10th International
  Symposium,  College Park, MD, USA,  19--24 June 2011; pp. 809--820.

\bibitem[McGrattan \em{et~al.}(2013)McGrattan, Hostikka, McDermott, Floyd,
  Weinschenk, and Overholt]{FDS_MathVal_Guides}
McGrattan, K.; Hostikka, S.; McDermott, R.; Floyd, J.; Weinschenk, C.;
  Overholt, K.
\newblock {\em {Fire Dynamics Simulator, Technical Reference Guide, Volume 1: Mathematical Model, Volume 3: Validation}}, 6th ed.;
\newblock National Institute of Standards and Technology: Gaithersburg,
  MD, USA;  VTT Technical Research Centre of Finland: Espoo, Finland, 2013.

\bibitem[Beyler(2016)]{SFPE:Beyler}
Beyler, C.
\newblock Flammability Limits of Premixed and Diffusion Flames. In {\em SFPE
  Handbook of Fire Protection Engineering}, 5th ed.;  \mbox{Hurley, M., Ed.;}
  Springer: New York, NY, USA, 2016.

\bibitem[Holman(1990)]{Holman:1}
Holman, J.
\newblock {\em Heat Transfer}, 7th ed.; McGraw-Hill: New York, NY, USA, 1990.

\bibitem[Incropera and De~Witt(1996)]{Incropera:1}
Incropera, F.P.; De~Witt, D.P.
\newblock {\em Fundamentals of Heat and Mass Transfer}, 4th ed.; John Wiley and
  Sons: New York,  NY, USA, 1996.

\bibitem[Berger(2017)]{berger_2016}
Berger, M.
\newblock Cut Cells: Meshes and Solvers.
\newblock {\em Handb. Numer. Anal.} {\bf 2017}, {\em 18},~1--22.
\newblock {doi:10.1016/bs.hna.2016.10.008}.

\bibitem[Eymard \em{et~al.}(2000)Eymard, Gallouet, and Herbin]{eymard_2000}
Eymard, R.; Gallouet, T.; Herbin, R.
\newblock Finite volume methods. In {\em Solution of Equation in Rn (Part 3),
  Techniques of Scientific Computing (Part 3)}; Handbook of Numerical Analysis;  Elsevier: Amsterdam, The Netherlands, 2000; Volume~7,  pp. 713 -- 1018.
\newblock {doi:10.1016/S1570-8659(00)07005-8}.

\bibitem[LeVeque(2002)]{leveque_2002}
\textls[-20]{LeVeque, R.
\newblock {\em Finite Volume Methods for Hyperbolic Problems}; Cambridge Texts
  in Applied Mathematics, Cambridge University Press: Cambridge, United Kingdom, 2002.}

>>>>

In the formal derivation of the LES equations (see, e.g,~\cite{Pope:2000,FDS_Tech_Guide}) the filtered nonlinear terms (advection terms, mean chemical source term, and~the unresolved boundary fluxes) require subgrid-scale parameterizations.  In~this section, LES filter notation, as well as Cartesian tensor index notation, are used to clarify the terms used in the governing~equations.

@@

Here, $D_F$ is the binary diffusivity of the fuel species in air, $k_{sgs}$ is the modeled subgrid kinetic energy per unit mass discussed above, and~$g$ is the gravitational acceleration. The~constant $C_u=0.4$ is determined by matching flame height correlations across a wide range of fire Froude numbers~\cite{FDS_Tech_Guide}.

@@

\textls[-20]{The unresolved heat flux at the surface, $\dot{q}_w''$, is determined using an \mbox{engineering approach}},
\begin{equation}
\dot{q}_w'' = h (T_g - T_w),
\end{equation}
where $h$ is the convective heat transfer coefficient, $T_w$ is the local temperature of the surface, and~$T_g$ is the temperature of the first gas phase cell off the wall.  Empirical natural/forced convection correlations are used to determine $h$:
\begin{equation}
h = \max \left[C\, |T_g-T_w|^{1/3} \; , \;
\frac{k}{L} \, \mathrm{Nu} \; , \;
\frac{k}{\delta n/2} \right],
\label{eq:qconv}
\end{equation}
where $C$ is a empirical coefficient for natural convection (1.52 for a horizontal plate and 1.31 for a vertical plane or cylinder)~\cite{Holman:1}, $L$ is a characteristic length related to the size of the physical obstruction, and~$k$ is the thermal conductivity of the gas. The~forced convection Nusselt number (Nu) depends on the geometry and flow characteristics~\cite{Holman:1,Incropera:1}.  Further details are provided in~\cite{FDS_Tech_Guide}.

@@

%\bibliography{Review_Process/FDS_refs,Review_Process/LOFM_Workshop_References,Review_Process/Vanella_Article_Atmosphere_2020}

@@

\bibitem[Thomas \em{et~al.}(2017)Thomas, Butry, Gilbert, Webb, and
  Fung]{thomas_2017}
Thomas, D.; Butry, D.; Gilbert, S.; Webb, D.; Fung, J.
\newblock The Costs and Losses of Wildfires: A Literature Review.
\newblock Special Publication NIST SP - 1215, National Institute of Standards
  and Technology, Gaithersburg, Mayland,  2017.
\newblock
  \href{https://www.nist.gov/publications/costs-and-losses-wildfires}{https://www.nist.gov/publications/costs-and-losses-wildfires} (accessed on 05/02/2021).

\bibitem[McDermott \em{et~al.}(2019)McDermott, Bryner, and
  Heintz]{mcdermott_2019}
McDermott, R.; Bryner, N.; Heintz, J.
\newblock Large Outdoor Fire Modeling (LOFM) Workshop Summary Report.
\newblock Special Publication NIST SP - 1245, National Institute of Standards
  and Technology, Gaithersburg, Mayland,  2019.
\newblock
  \href{https://www.nist.gov/publications/large-outdoor-fire-modeling-lofm-workshop-summary-report}{https://www.nist.gov/publications/large-outdoor-fire-modeling-lofm-workshop-summary-report} (accessed on 05/02/2021).

\bibitem[Richards \em{et~al.}(2020)Richards, Brew, and Smith]{richards_2020}
Richards, L.; Brew, N.; Smith, L.
\newblock 2019–20 Australian bushfires—frequently asked questions: a quick
  guide.
\newblock Research Paper Series 2019-20, ISSN 2203-5249, Parliament of
  Australia, Canberra, Australia,  2020.
\newblock
  \href{https://parlinfo.aph.gov.au/parlInfo/download/library/prspub/7234762/upload\_binary/7234762.pdf}{https://parlinfo.aph.gov.au/parlInfo/download/library/prspub/7234762/upload\_binary/7234762.pdf} (accessed on 05/02/2021).

\bibitem[Papadopoulos and Niovi~Pavlidou(2011)]{Papadopoulos_2011}
Papadopoulos, G.D.; Niovi~Pavlidou, F.
\newblock A review of a new generation of wildfire–atmosphere modeling.
\newblock {\em IEEE Systems Journal} {\bf 2011}, {\em 5},~233--243.

\bibitem[Bakhshaii and Johnson(2019)]{Bakhshaii_2019}
Bakhshaii, A.; Johnson, E.
\newblock A review of a new generation of wildfire–atmosphere modeling.
\newblock {\em Canadian Journal of Forest Research} {\bf 2019}, {\em
  49},~565--574.

\bibitem[Rothermel(1972)]{Rothermel:1972}
Rothermel, R.C.
\newblock A mathematical model for predicting fire spread in wildland fuels.
\newblock Technical Report INT-115, USDA Forest Service, Ogden, Utah,  1972.
\newblock
  \href{http://www.treesearch.fs.fed.us/pubs/32533}{http://www.treesearch.fs.fed.us/pubs/32533} (accessed on 05/02/2021).

\bibitem[Anderson(1982)]{Anderson:1982}
Anderson, H.
\newblock {Aids to Determining Fuel Models for Estimating Fire Behavior}.
\newblock General Technical Report INT-122, Intermountain Forest and Range
  Experiment Station, USDA Forest Service, Ogden, Utah,  1982.
\newblock
  \href{https://www.fs.usda.gov/treesearch/pubs/6447}{https://www.fs.usda.gov/treesearch/pubs/6447} (accessed on 05/02/2021).

\bibitem[Finney(2004)]{Finney:FARSITE}
Finney, M.
\newblock {Fire Area Simulator – Model, Development and Evaluation}.
\newblock Research Paper RMRS-RP-4 Revised, United States Forest Service, Rocky
  Mountain Research Station, Missoula, Montana,  2004.
\newblock
  \href{http://www.fs.fed.us/rm/pubs/rmrs\_rp004.pdf}{http://www.fs.fed.us/rm/pubs/rmrs\_rp004.pdf} (accessed on 05/02/2021).

\bibitem[Bova \em{et~al.}(2015)Bova, Mell, and Hoffman]{Bova:IJWF2015}
Bova, A.; Mell, W.; Hoffman, C.
\newblock {A comparison of level set and marker methods for the simulation of
  wildland fire front propagation}.
\newblock {\em International Journal of Wildland Fire} {\bf 2015}, {\em
  25},~229--241.
\newblock
  \href{http://dx.doi.org/10.1071/WF13178}{http://dx.doi.org/10.1071/WF13178} (accessed on 05/02/2021).

\bibitem[McGrattan \em{et~al.}(2013)McGrattan, Hostikka, McDermott, Floyd,
  Weinschenk, and Overholt]{FDS_Users_Guide}
McGrattan, K.; Hostikka, S.; McDermott, R.; Floyd, J.; Weinschenk, C.;
  Overholt, K.
\newblock {\em {Fire Dynamics Simulator, User's Guide}}.
\newblock National Institute of Standards and Technology, Gaithersburg,
  Maryland, USA, and VTT Technical Research Centre of Finland, Espoo, Finland,
  sixth ed.,  2013.

\bibitem[Coen(2013)]{Coen:2}
Coen, J.L.
\newblock {Modeling Wildland Fires: A Description of the Coupled
  Atmosphere-Wildland Fire Environment Model (CAWFE)}.
\newblock Technical Report NCAR/TN500+STR, National Center for Atmospheric
  Research, Boulder, CO,  2013.

@@

\bibitem[Lautenberger(2013)]{LAUTENBERGER_2013}
Lautenberger, C.
\newblock Wildland fire modeling with an Eulerian level set method and
  automated calibration.
\newblock {\em Fire Safety Journal} {\bf 2013}, {\em 62},~289 -- 298.
\newblock
  \href{https://doi.org/10.1016/j.firesaf.2013.08.014}{https://doi.org/10.1016/j.firesaf.2013.08.014} (accessed on 05/02/2021).

\bibitem[Coen \em{et~al.}(2013)Coen, Cameron, Michalakes, Patton, Riggan, and
  Yedinak]{coen_2013}
Coen, J.L.; Cameron, M.; Michalakes, J.; Patton, E.G.; Riggan, P.J.; Yedinak,
  K.M.
\newblock WRF-Fire: Coupled Weather–Wildland Fire Modeling with the Weather
  Research and Forecasting Model.
\newblock {\em Journal of Applied Meteorology and Climatology} {\bf 2013}, {\em
  52},~16--38.
\newblock
  \href{https://doi.org/10.1175/JAMC-D-12-023.1}{https://doi.org/10.1175/JAMC-D-12-023.1} (accessed on 05/02/2021).

\bibitem[Mandel \em{et~al.}(2009)Mandel, Beezley, Coen, and Kim]{Mandel:2009}
Mandel, J.; Beezley, J.D.; Coen, J.L.; Kim, M.
\newblock {Data assimilation for wildland fires: Ensemble Kalman filters in
  coupled atmosphere-surface models}.
\newblock {\em IEEE Control Systems Magazine} {\bf 2009}, {\em 9},~47–65.
\newblock
  \href{https://doi.org/10.1109/MCS.2009.932224}{https://doi.org/10.1109/MCS.2009.932224} (accessed on 05/02/2021).

\bibitem[Mandel \em{et~al.}(2011)Mandel, Beezley, and Kochanski]{Mandel:2011}
Mandel, J.; Beezley, J.D.; Kochanski, A.K.
\newblock {Coupled atmosphere-wildland fire modeling with WRF 3.3 and SFIRE
  2011}.
\newblock {\em Geosci. Model Dev.} {\bf 2011}, {\em 4},~591--610.
\newblock
  \href{https://doi.org/10.5194/gmd-4-591-2011}{https://doi.org/10.5194/gmd-4-591-2011} (accessed on 05/02/2021).

\bibitem[Mandel \em{et~al.}(2015)Mandel, Amram, Beezley, Kelman, Kochanski,
  Kondratenko, Lynn, Regev, and Vejmelka]{Mandel:2014}
Mandel, J.; Amram, S.; Beezley, J.D.; Kelman, G.; Kochanski, A.K.; Kondratenko,
  V.Y.; Lynn, B.H.; Regev, B.; Vejmelka, M.
\newblock {Recent advances and applications of WRF-SFIRE}.
\newblock {\em Nat. Hazards Earth Syst. Sci.} {\bf 2015}, {\em 14},~2829--2845.
\newblock
  \href{https://doi.org/10.5194/nhess-14-2829-2014}{https://doi.org/10.5194/nhess-14-2829-2014} (accessed on 05/02/2021).

\bibitem[Kochanski \em{et~al.}(2016)Kochanski, Jenkins, Yedinak, Mandel,
  Beezley, and Lamb]{Kochanski:2016}
Kochanski, A.K.; Jenkins, M.A.; Yedinak, K.; Mandel, J.; Beezley, J.; Lamb, B.
\newblock {Toward an integrated system for fire, smoke, and air quality
  simulations}.
\newblock {\em Int. J. Wildland Fire} {\bf 2016}, {\em 25},~534–546.
\newblock
  \href{https://doi.org/10.1071/WF14074}{https://doi.org/10.1071/WF14074} (accessed on 05/02/2021).

\bibitem[Sethian(1999)]{Sethian:1999}
Sethian, J.A.
\newblock {\em Level Set Methods and Fast Marching Methods: Evolving Interfaces
  in Computational Geometry, Fluid Mechanics, Computer Vision, and Materials
  Science}; Cambridge,  1999.

\bibitem[Osher and Fedkiw(2006)]{Osher:2006}
Osher, S.; Fedkiw, R.
\newblock {\em Level Set Methods and Dynamic Implicit Surfaces}; Springer,
  2006.

\bibitem[Mell \em{et~al.}(2007)Mell, Jenkins, Gould, and Cheney]{Mell:IJWF2007}
Mell, W.; Jenkins, M.; Gould, J.; Cheney, P.
\newblock {A physics-based approach to modelling grassland fires}.
\newblock {\em International Journal of Wildland Fire} {\bf 2007}, {\em
  16},~1--22.

@@

\bibitem[Arca \em{et~al.}(2019)Arca, G., M., M., and P.]{Arca_2019}
Arca, B.; G., T.; M., C.; M., S.; P., D.
\newblock A web-based wildfire simulator for operational applications.
\newblock {\em International Journal of Wildland Fire} {\bf 2019}, {\em
  28},~99--112.

\bibitem[Rehm and Baum(1978)]{Rehm:1}
Rehm, R.; Baum, H.
\newblock {The Equations of Motion for Thermally Driven, Buoyant Flows}.
\newblock {\em Journal of Research of the NBS} {\bf 1978}, {\em 83},~297--308.

\bibitem[McDermott and Floyd(2015)]{McDermott:2015}
McDermott, R.; Floyd, J.
\newblock {Enforcing realizability in explicit multi-component species
  transport}.
\newblock {\em Fire Safety Journal} {\bf 2015}, {\em 78},~180--187.

\bibitem[McDermott(2014)]{mcdermo_2014}
McDermott, R.J.
\newblock A velocity divergence constraint for large-eddy simulation of
  low-Mach flows.
\newblock {\em Journal of Computational Physics} {\bf 2014}, {\em
  274},~413--431.
\newblock
  \href{http://dx.doi.org/10.1016/j.jcp.2014.06.019}{http://dx.doi.org/10.1016/j.jcp.2014.06.019} (accessed on 05/02/2021).

\bibitem[Pope(2000)]{Pope:2000}
Pope, S.B.
\newblock {\em Turbulent Flows}; Cambridge University Press,  2000.

\bibitem[McGrattan \em{et~al.}(2013)McGrattan, Hostikka, McDermott, Floyd,
  Weinschenk, and Overholt]{FDS_Tech_Guide}
McGrattan, K.; Hostikka, S.; McDermott, R.; Floyd, J.; Weinschenk, C.;
  Overholt, K.
\newblock {\em {Fire Dynamics Simulator, Technical Reference Guide}}.
\newblock National Institute of Standards and Technology, Gaithersburg,
  Maryland, USA, and VTT Technical Research Centre of Finland, Espoo, Finland,
  sixth ed.,  2013.
\newblock Vol.~1: Mathematical Model; Vol.~2: Verification Guide; Vol.~3:
  Validation Guide; Vol.~4: Software Quality Assurance.

\bibitem[Poinsot and Veynante(2005)]{Poinsot:TNC}
Poinsot, T.; Veynante, D.
\newblock {\em {Theoretical and Numerical Combustion}}, 2nd ed.; R.T. Edwards,
  Inc.: Philadelphia, Pennsylvania,  2005.

\bibitem[Deardorff(1980)]{Deardorff:1980}
Deardorff, J.
\newblock {Stratocumulus-capped mixed layers derived from a three-dimensional
  model}.
\newblock {\em Boundary-Layer Meteorol.} {\bf 1980}, {\em 18},~495--527.

@@

\bibitem[Bardina \em{et~al.}(1980)Bardina, Ferziger, and
  Reynolds]{Bardina:1980}
Bardina, J.; Ferziger, J.H.; Reynolds, W.C.
\newblock {Improved Subgrid Scale Models for Large Eddy Simulation}.
\newblock  AIAA 13th Fluid \& Plasma Dynamics Conference; American Institute of
  Aeronautics and Astronautics, ,  1980; AIAA-80-1357.

\bibitem[Nicoud and Ducros(1999)]{Nicoud:1999}
Nicoud, F.; Ducros, F.
\newblock {Subgrid-Scale Stress Modelling Based on the Square of the Velocity
  Gradient Tensor}.
\newblock {\em Flow, Turbulence, and Combustion} {\bf 1999}, {\em
  62},~183--200.

\bibitem[Maragkos and Merci(2020)]{Maragkos:2020}
Maragkos, G.; Merci, B.
\newblock On the use of dynamic turbulence modelling in fire applications.
\newblock {\em Comb. and Flame} {\bf 2020}, {\em 216},~9--23.

@@

\bibitem[Magnussen and Hjertager(1977)]{Magnussen:1}
Magnussen, B.; Hjertager, B.
\newblock {On Mathematical Modeling of Turbulent Combustion with Special
  Emphasis on Soot Formation and Combustion}.
\newblock  Proceedings of the Sixteenth Symposium (International) on
  Combustion. Combustion Institute, Pittsburgh, Pennsylvania,  1977, pp.
  719--729.

\bibitem[McDermott \em{et~al.}(2011)McDermott, McGrattan, and
  Floyd]{McDermott:2011}
McDermott, R.; McGrattan, K.; Floyd, J.
\newblock A Simple Reaction Time Scale for Under-Resolved Fire Dynamics.
\newblock  Fire Safety Science -- Proceedings of the 10th International
  Symposium; ,  2011; pp. 809--820.

\bibitem[Beyler(2016)]{SFPE:Beyler}
Beyler, C.
\newblock Flammability Limits of Premixed and Diffusion Flames. In {\em SFPE
  Handbook of Fire Protection Engineering}, 5th ed.;  Hurley, M., Ed.;
  Springer: New York,  2016.

\bibitem[Holman(1990)]{Holman:1}
Holman, J.
\newblock {\em Heat Transfer}, 7th ed.; McGraw-Hill: New York,  1990.

\bibitem[Incropera and De~Witt(1996)]{Incropera:1}
Incropera, F.P.; De~Witt, D.P.
\newblock {\em Fundamentals of Heat and Mass Transfer}, 4th ed.; John Wiley and
  Sons: New York,  1996.

\bibitem[Berger(2017)]{berger_2016}
Berger, M.
\newblock Cut Cells: Meshes and Solvers.
\newblock {\em Handbook of Numerical Analysis} {\bf 2017}, {\em 18},~1--22.
\newblock
  \href{https://doi.org/10.1016/bs.hna.2016.10.008}{https://doi.org/10.1016/bs.hna.2016.10.008} (accessed on 05/02/2021).

\bibitem[Eymard \em{et~al.}(2000)Eymard, Gallouet, and Herbin]{eymard_2000}
Eymard, R.; Gallouet, T.; Herbin, R.
\newblock Finite volume methods. In {\em Solution of Equation in Rn (Part 3),
  Techniques of Scientific Computing (Part 3)}; Elsevier,  2000; Vol.~7, {\em
  Handbook of Numerical Analysis}, pp. 713 -- 1018.
\newblock
  \href{https://doi.org/10.1016/S1570-8659(00)07005-8}{https://doi.org/10.1016/S1570-8659(00)07005-8} (accessed on 05/02/2021).

\bibitem[LeVeque(2002)]{leveque_2002}
LeVeque, R.
\newblock {\em Finite Volume Methods for Hyperbolic Problems}; Cambridge Texts
  in Applied Mathematics, Cambridge University Press,  2002.

\bibitem[Balaras(2004)]{balaras_2004}
Balaras, E.
\newblock Modeling complex boundaries using an external force field on fixed
  Cartesian grids in large-eddy simulations.
\newblock {\em Computers \& Fluids} {\bf 2004}, {\em 33},~375 -- 404.

\bibitem[LeVeque(2007)]{leveque2007finite}
LeVeque, R.
\newblock {\em Finite Difference Methods for Ordinary and Partial Differential
  Equations: Steady-State and Time-Dependent Problems}; Other Titles in Applied
  Mathematics, Society for Industrial and Applied Mathematics,  2007.
